Equation-of-state insensitive relations after GW170817

### 2019-02-23 paper/bin-love-after-gw170817.tex
katerina comments sec 2

\begin{figure*}
\begin{center} 
\includegraphics[width=.97\columnwidth]{EoSs.eps}
\includegraphics[width=\columnwidth]{hybridEoSs.eps}
\end{center}
\caption{(Color Online) Left: Small representative samples of the unconstrained (dotted) and constrained (solid) sets, together with the 90\% marginalized posterior distribution from the observation of GW170817 (cyan shaded region)~\cite{LIGO:posterior}. Observe that the there is significantly less variability in the constrained set of EoSs due to the requirement that they be consistent with the GW170817 observation. Right: EoSs for ACS and ACB hybrid stars, each transitioning from a hadronic branch (corresponding to a pure hadronic-matter NS) into a quark-matter branch (quark-matter inner core surrounded by hadronic matter) at various transition pressures $P_{\text{tr}}$.
}
\label{fig:eos}
\end{figure*}

@@

The unconstrained set is then defined by drawing random samples in the spectral coefficients (within their allowed prior ranges), and then eliminating any EoS that either leads to a polytropic index $\Gamma$ outside the allowed range, breaks the causality restriction, or breaks the maximum mass restriction. The constrained set is defined in a similar way, with the addition of the restriction that the resulting EoS be inside the 90\% marginalized posterior distribution on the pressure-mass density plane derived from the GW170817 observation~\cite{LIGO:posterior,Carney:2018sdv}  (see Fig.~2 in~\cite{LIGO:posterior}). In both cases, each set consists of 100 members, with a subset of these shown in the left panel of Fig.~\ref{fig:eos}.

>>>>

\begin{figure*}
\begin{center} 
\includegraphics[width=.97\columnwidth]{EoSs.eps}
\includegraphics[width=\columnwidth]{hybridEoSs.eps}
\end{center}
\caption{(Color Online) Left: Small representative samples of the unconstrained (dotted) and constrained (solid) sets, together with the 90\% marginalized posterior distribution from the observation of GW170817 (cyan shaded region)~\cite{LIGO:posterior}. There is significantly less variability in the constrained set of EoSs due to the requirement that they be consistent with the GW170817 observation. Right: EoSs for ACS and ACB hybrid stars, each transitioning from a hadronic branch (corresponding to a pure hadronic-matter NS) into a quark-matter branch (quark-matter inner core surrounded by hadronic matter) at various transition pressures $P_{\text{tr}}$.
}
\label{fig:eos}
\end{figure*}

@@

The unconstrained set is then defined by drawing random samples in the spectral coefficients (within their allowed prior ranges), and then eliminating any EoS that either leads to a polytropic index $\Gamma$ outside the allowed range, breaks the causality restriction, or breaks the maximum mass restriction. The constrained set is defined in a similar way, with the addition of the restriction that the resulting EoS be inside the 90\% marginalized posterior distribution on the pressure-mass density plane derived from the GW170817 observation~\cite{LIGO:posterior,Carney:2018sdv}  (see Fig.~2 in~\cite{LIGO:posterior}). In both cases, each set consists of 100 members, with a subset of these shown in the left panel of Fig.~\ref{fig:eos}.\kc{wait, aren't you using the samples that Calr sent you directly? If yes we need to describe how they were computed and add the appropriate citations to code and data. But that's not what you are describing here}
